\let\textcircled=\pgftextcircled
\chapter{Quality Assurance Criteria}

\initial{Q}uality Assurance is the processes that transpire during the development of a software solution that are taken to ensure the product meets contractual obligations and needs of the client.  The quality of the product will be judged on the efficiency and effectiveness of facilitating transactions across businesses, and whether they can tokenise their assets, fungible, and transfer them across to other businesses. \\

The application needs to be reliable and not ‘crash’ during function as this would prove detrimental to the requirement for the blockchain to be always running. The system that is created needs to have very high security as it will manage a large quantity of transactions, possibly facilitating billions of dollars in transaction execution. This security is inherent to how the system is built as the consensus mechanisms, the runtime modules are all built in a way that makes it almost impossible to break, this is combined with the decentralised, private nature of the network, allowing businesses to not have to trust a central authorities server.  Further, the business blockchain must have an easy-to-use front end that will be used by non-technical employees, however, setting up of the node will need to be undertaken by a development team. More specifically the buttons, forms and layout must be easily navigable and consistent. Finally, the system must go through modular and systematic testing to make sure all components work in unison and function in the way the client wishes. 

