\let\textcircled=\pgftextcircled
\chapter{Social and Ethical Issue}

\initial{T}he development and design of software solutions carries the weight of being socially and ethically responsible. The social and ethical issues surrounding this application are privacy and inclusivity. Privacy is about protecting an individual’s personal information. Personal information is any information that allows others to identify you. Privacy is a fundamental principle of our society, we have the right to know who holds our personal information. In Australia, privacy is legally protected under the Privacy Act 1988 and its subsequent amendments. This act contains ten National Privacy Principles, that set standards that organisations are required to meet when dealing with personal. As the Application is developed and operated from Australia, it needs to follow these privacy laws and obligations. This issue applies to this application the collection of data such as location, preferences, budgets are private and the distribution of that data, such as locations that are being visited needs to be carefully monitored and restricted. The data from this application must be encrypted within a database so that unwanted access to the user database would not mean that all user data is exposed. Another very significance appearance of privacy issues within Traverse is the transference of payment details. These financial details would need to be encrypted and communicated over a TLS stream to ensure security. As this is extremely sensitive information any critical issue within the software needs to be resolved in a timely, accurate and efficient manner.  \\

Another social and ethical issue is the inclusivity of the application as software design should include functionality that allows software to be used and accessed by a wide range of users. People who are visually or physically impaired need to have accessibility functions that allow them to utilise the software. This means that certain transport or activities need to consider the physical abilities of the individual before recommending it to them.
